OpenMPIR

### 2017-09-08 paper.tex
changed back to barcelona openmp task suite

\begin{abstract}
Optimizing compilers for task-level parallelism are still in their infancy.
This work explores a compiler front end that translates OpenMP tasking semantics to Tapir,
an extension to LLVM IR that represents fork-join parallelism. This enables
analyses and optimizations that were previously inaccessible to OpenMP codes,
as well as the ability to target additional runtimes at code generation. Using
a Cilk runtime back end, we compare results to existing OpenMP implementations.
Initial performance results for the Barcelona OpenMP tasking suite show
performance improvements over existing implementations.
\end{abstract}

@@

With fragmentation comes questions of compatibility or composability of 
different programming models. To illustrate this, consider the example of
a program using a library that uses OpenMP to implement parallelism internally. 
If this program uses a different programming model for parallelism, e.g.\ Cilk,
there is currently no good solution for ensuring that the two different back ends
will cooperate with management of hardware resources. 
%
Addressing these concerns is a major motivation for our use of Tapir.  By
standardizing an IR, in addition to easing the development of optimizations,
one avoids duplicating work across different implementations. It also enables
the possibility of multiple programming models coexisting peacefully. We will
return to this consideration later in Section~\ref{Sec:Discussion} when discussing
future work.

\section{Tapir} \label{Sec:Tapir}
Tapir is an extension to LLVM proposed by Schardl, Moses, and Leiserson
seeking to resolve issues in optimizing parallel code. Prior to
the introduction of Tapir compilers would represent parallel programs
by directly translating their syntax to opaque runtime calls. This allowed
compilers to support parallel programs but meant that traditional 
optimizations such as code motion~\cite{} or common-subexpression elimination~\cite{}
weren't able to reason about parallel programs. This often led to parallel
programs running significantly slower than expected. In the Tapir project
the authors show that it is possible to represent and optimize fork-join
parallel programs with relatively minimal modifications to the compiler, namely
the introduction of three instructions designed to interface well with an
existing compiler.

>>>>

\begin{abstract}
Optimizing compilers for task-level parallelism are still in their infancy.
This work explores a compiler front end that translates OpenMP tasking
semantics to Tapir, an extension to LLVM IR that represents fork-join
parallelism. This enables analyses and optimizations that were previously
inaccessible to OpenMP codes, as well as the ability to target additional
runtimes at code generation. Using a Cilk runtime back end, we compare results
to existing OpenMP implementations.  Initial performance results for the
Barcelona OpenMP task suite show performance improvements over existing
implementations.
\end{abstract}

@@

With fragmentation comes questions of compatibility or composability of 
different programming models. To illustrate this, consider the example of
a program using a library that uses OpenMP to implement parallelism internally. 
If this program uses a different programming model for parallelism, e.g.\ Cilk,
there is currently no good solution for ensuring that the two different back ends
will cooperate with management of hardware resources.

Addressing these concerns is a major motivation for our use of Tapir.  By
standardizing an IR, in addition to easing the development of optimizations,
one avoids duplicating work across different implementations. It also enables
the possibility of multiple programming models coexisting peacefully. We will
return to this consideration later in Section~\ref{Sec:Discussion} when
discussing future work.

\section{Tapir} \label{Sec:Tapir}
Tapir is an extension to LLVM proposed by Schardl, Moses, and Leiserson
seeking to resolve issues in optimizing parallel code. Prior to
the introduction of Tapir compilers would represent parallel programs
by directly translating their syntax to opaque runtime calls. This allowed
compilers to support parallel programs but meant that traditional 
optimizations such as code motion or common-subexpression elimination weren't
able to reason about parallel programs. This often led to parallel programs
running significantly slower than expected. In the Tapir project the authors
show that it is possible to represent and optimize fork-join parallel programs
with relatively minimal modifications to the compiler, namely the introduction
of three instructions designed to interface well with an existing compiler.
